%-------------------------------------------------------------------------------
\cvsection{Conferences \& Publications}		%	SECTION TITLE


%---------------------------------------------------------



\begin{cvparagraph}

\begin{itemize}[label=$\S$]

\item {{\it Tomar P.} , Mariarosaria M.  “FVIII: A crucial hemostatic factor to control bleeding'' article published in EDUC8 Blog on Feb 2021}

\item {Mariarosaria M, Nardini E. , {\it Tomar P.} , Scatigna S. “Blood coagulation FVIII: An overview”, article published in EDUC8 Blog, May 2021}

\item {International Society on Thrombosis and Haemostasis (ISTH) virtual congress, 17 - 21 July, 2021}

\item {European Association for Haemophilia and Allied Disorders (EAHAD) virtual congress, 3 -5 Feb, 2021.}

\item {Dubey R, Mishra V, {\it Tomar P.} Duality relations for second-order programming problem under (G, αf)-bonvexity assumptions, Asian-European Journal of Mathematics Vol. 13, No. 1 (2020) 2050044 (17 pages) c World Scientific Publishing Company, DOI: 10.1142/S1793557120500448}

\item {{\it Puneet Tomar}, "Cooperation in Multistage and Repeated Hierarchical Games", twelveth International Conference on Game Theory and Management, a three-day conference, St. Petersburg, Russia, June 27-29, 2018.}

\item {Li Yin, {\it Puneet Tomar}, "Construction Of M-Strongly Time-Consistent Sub-core In the Game with Spanning Tree", The Twelfth International Conference on Game Theory and Management, a three-day conference, St. Petersburg, Russia, June 27-29, 2018.}

\item {{\it Puneet Tomar}, Sheifali Gupta, Amanpreet Kaur, Sweety Dabbas, D M Akbar Hussain, “Low Power FPGA-Based Solar Charge Sensor Design Using Frequency Scaling”, Gyancity Journal of Electronics and Computer Science, Vol.1, No.1, pp.25-28, September 2016, ISSN: 2446–2918 DOI: 10.21058/gjecs.2016.11005.}

\item {Pandey S, {\it Tomar P}, Verma G, “Design of Energy Efficient Sinusoidal PWM Waveform Generator on FPGA”, 3rd International Conference on Green Computing and Engineering Technologies (ICGCET), The Killaloe Hotel, Kincora Harbour, Killaloe, County Clare, Ireland, 08-10 August 2017.}

\item {Sethi K., {\it Tomar P.} and Pandey B., “Environment-Friendly Air Conditioner Design Using Cooling Pot and Solar Panel”, 50th Golden Jubilee Annual Convention on “Digital Life”, 02-05 December 2015, New Delhi.}

 
\end{itemize}


\end{cvparagraph}
